### 2020-04-04 04-CCNA.tex
small corrections
Update 04-CCNA.tex

In this section we introduce  the syntax and operational semantics
of a variant of the {\tt link}-calculus~\cite{BodeiBB12}, the c\CNA\  (chained \CNA)
where the prefixes are link chains.
%In this section we just focus on the basic ideas of link
% interaction, while we shall enhance the model with name mobility in
% the next section.

@@

Virtual links represent missing elements of a chain. 
The equivalence $\blackstretcheq$ models expansion/contraction of virtual links to adjust the length of a link chain.

>>>>

In this section we introduce  the syntax and operational semantics
of a variant of the {\tt link}-calculus~\cite{BodeiBB12}, the c\CNA\  (chained \CNA)
where the prefixes are link chains and not just links.
%In this section we just focus on the basic ideas of link
% interaction, while we shall enhance the model with name mobility in
% the next section.

@@

Virtual links represent missing elements of a chain. 
A chain is called \emph{solid} if it does not contain any virtual link.
The equivalence $\blackstretcheq$ models expansion/contraction of virtual links to adjust the length of a link chain.
